Stack Safety as a Security Property

### 2020-07-03 main.tex
typo
wip

While integrity and confidentiality are relatively standard security
properties, the stack-safety setting raises an interesting additional
challenge:
the notion of who the attacker is shifts throught execution. Not only
does a caller need to be protected from its callee, but the callee
itself needs to be proteced from {\em its} callees.
We address this challenge by varying the observation power\apt{is this
  the right word? doesn't it conflict with our later use of ``observation''?}
of the attacker at call points, and demonstrate that our policy is
implementable by pre-existing monitoring mechanisms. \bcp{The two parts of
  the sentence are about two very different things.  The second deserves its
  own paragraph, IMO.}\apt{+1}

@@

\begin{figure}[b]
  \begin{centering}
    \begin{minipage}{.3\textwidth}
\begin{verbatim}
main = {
  int x -42, y = 0;
  y = g(0);
  print (x + y);
}
\end{verbatim}
    \end{minipage}
    \begin{minipage}{.3\textwidth}
\begin{verbatim}
g(z) = {
  int w = h(17);
  print z;
  return (z + w);
}
\end{verbatim}
    \end{minipage}
    \begin{minipage}{.3\textwidth}
\begin{verbatim}
h(v) = {
  return (v + 1);
}

>>>>

\bcp{``alternative framework that uses the conceptual framework of language-based security''}
\bcp{idea:intrinsic vs. extrinsic: stktokens only talks}

Another dimension: spatial vs temporal safety

While integrity and confidentiality are relatively standard security
properties, the stack-safety setting raises an interesting additional
challenge:
the notion of who the attacker is shifts throught execution. Not only
does a caller need to be protected from its callee, but the callee
itself needs to be proteced from {\em its} callees.
We address this challenge by varying the access powers
of the attacker at call points, and demonstrate that our policy is
implementable by pre-existing monitoring mechanisms. \bcp{The two parts of
  the sentence are about two very different things.  The second deserves its
  own paragraph, IMO.}\apt{+1}

@@

\begin{figure}[b]
  \begin{centering}
    \begin{minipage}{.3\textwidth}
\begin{verbatim}
main = {
  int x = 42, y = 0;
  y = g(0);
  print (x + y);
}
\end{verbatim}
    \end{minipage}
    \begin{minipage}{.3\textwidth}
\begin{verbatim}
g(z) = {
  int w = h(17);
  print z;
  return (z + w);
}
\end{verbatim}
    \end{minipage}
    \begin{minipage}{.3\textwidth}
\begin{verbatim}
h(v) = {
  return (v + 1);
}
